Sparse Word Embedding for Multi-domain Machine Translation

### 2018-11-12 2019/naacl/naaclhlt2019.tex
naacl

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\begin{document}
\maketitle
\begin{abstract}
\end{abstract}

\section{Introduction}

@@

\section{The Model}
There is not any changes in the architecture of Neural Machine Translation network except the construction of word embedding.

\section{Experiments}

\subsection{Corpora}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2019}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{url}
\usepackage{float} 
%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\begin{document}
\maketitle
\begin{abstract}
In this paper, we introduce an application of an old technique \cite{P07-1033} in Multi-Domain Neural Machine Translation.  By defining general information encoding region and domain-specific encoding region in word embedding vector, we are able to  seperate domain-related information flows in forward and backward propagation during training
mitigate the catastrophic interference happens between the inference of different domains in Neural Machine Translation system, i.e to improve the performance of the system for every domain in which it was trained. 
\end{abstract}

\section{Introduction}
Despite fast improvement thanks to new architectures \cite{NIPS2017_7181} \cite{bahdanau2014neural} \cite{D13-1176} \cite{Sutskever2014Sequence}, Machine Translation still struggles with data scarcity. Domain adaptation, or it's special case Multi-domain, is the situation where in-domain data for example banking is rare while out-domain data such as news are plenty, one aims to leverage out-domain data to improve quality of Machine Translation system which is perfectible while being trained with small in-domain dataset. The problem is that we have not been able to apply Domain-adaptation to several domains at once, i.e to build one model which is best for several domains. It is obvious to realize that the bias to in-domain dataset makes model worse in translating other domains. This phenomenon can be implied by well-known problem in Machine Learning, Catastrophic Interference \cite{Michael1989Catastrophic}. In Multi-domain Machine Translation, one have to deal with polysemies whose meaning can be totally different in different domains, for example, the word "chair" means an household tool in "if you are taking a medicine which may cause low blood pressure when rising from a chair or bed " (extracted from medical corpora EMEA \cite{Tiedemann2009RANLP5}) while the word "chair" means to preside over a meeting in following sentence "The President of the ECB or , in his absence , the Vice-President , chairs the meetings of the Governing Council , the Executive Board and the General Council of the ECB. " (extracted from European Central Bank corpora \cite{Tiedemann2009RANLP5}). Using the same word embedding for polysemy obstructs the model from differentiating the meaning of a polysemy in one domain from it's other meaning in the other domain.

@@

\section{The Model}
There is not any changes in the architecture of Neural Machine Translation network except the construction of word embedding. 
\begin{figure}[h]
\center
    \includegraphics[width=0.8\linewidth]{Sparse1}
    \caption{Illustration of the model.} 
    \label{network}
\end{figure}
\section{Experiments}

\subsection{Corpora}
To evaluate the performance of proposed architecture, we use 4 corpora for training: European Medicines Agency; European Central Bank, News-commentary and European Parliament \cite{Tiedemann2009RANLP5} corresponding to 4 domains: medical, banking, news and administrative  respectively and one non-domain corpora Common-crawl  which was introduced in Shared Task: Machine Translation of News the Third Conference On Machine Translation 2018(WMT2018). We use Khresmoi-dev, a test set used in the Biomedical Translation Task (WMT2018), newstest2008, and test2006 as validation set for domains: medical, news administrative; except for banking domain, we use a subset of size 2000 extracted from original corpora and excluded from training set. To test the model, we use Khresmoi-test; newstest2009 and test2007 for domains: medical, news administrative; except for banking domain, we use a subset of size 2000 extracted from original corpora and excluded from training set. The information of used corpora is presented in table \ref{table:Corpora}
\begin{table}[H]
\resizebox{\columnwidth}{!}{
\begin{tabular}{ |l|l|l|l|l|l| }
\hline
Task & Corpora & Train & Dev & Test & Vocabulary \\ \hline
\multirow{5}{*}{$English \rightarrow French$} & European Medicines Agency & 1092568 & 500 & 1000 & \\
 & European Central Bank & 195960 & 2000 & 2000 &\\
 & News-commentary & 258432 & 2051 & 3027 & \\
 & European Parliament & 2007723 & 2000 & 2000 & \\
 & Common-crawl & 3244152 &  &  & \\ \hline
\multirow{5}{*}{$English \rightarrow German$} & European Medicines Agency & 1108752 & 500 & 1000 & \\
 & European Central Bank & 113174 & 2000 & 2000 &\\
 & News-commentary & 270769 & 2051 & 2525 & \\
 & European Parliament & 1920209 & 2000 & 2000 & \\ 
 & Common-crawl & 2399123 &  &  & \\ \hline
\hline
\end{tabular}
}
\caption{Corpora}
\label{table:Corpora}
\end{table}
